### 2023-03-24 resilience.tex
Up
up

\begin{theorem}\label{down-up}
Let $\mathscr{S}=(S,\rightarrow, \leq)$ be a completion-post-effective $\omega^2$-WSTS with strong compatibility and two finite \alain{non, confusion entre ensemble et base} sets: $\Bad$ and $\Safe$.
The resilience problem (RP) and the bounded resilience problem (BRP) are decidable.
\end{theorem}

@@

\begin{proof}
To decide the kRP, we may compare the input $k$ with $K=max(k_a \mid a=1,..,m \times n)$.
	If $k \geq K$, we conclude that 
$k$-resilience holds.
	If $k < K$, then we can answer the question by checking every paths of length smaller
	than $K$ from the $J_i$ in the completion.
\end{proof}

>>>>

\begin{theorem}\label{down-up}
Let $\mathscr{S}=(S,\rightarrow, \leq)$ be a completion-post-effective $\omega^2$-WSTS with strong compatibility and two 
%finite \alain{non, confusion entre ensemble et base}
 sets $\Bad = \downarrow \Bad$ and $\Safe = \uparrow \Safe$.
The resilience problem (RP) and the bounded resilience problem (BRP) are decidable.
\end{theorem}

@@

\begin{proof}
To decide the kRP, we may compare the input $k$ with $K=max(k_a \mid a=1,..,m \times n)$.
	If $k \geq K$, we conclude that 
$k$-resilience holds.
	If $k < K$, then we can answer the question by checking every paths of length smaller
	than $K$ from the ideals of the decomposition of $\Bad$ in the completion.
\end{proof}
